Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-03-08 paper/paper.tex

\ccsdesc{Music, Typing Efficiency} %May not need this
\keywords{Typing Efficiency with Music, Cognitive Function} % placeholder text for the time being
\maketitle

@@

\section{Methodoloy}
methods
test\cite{AudioDistractionsAshley}

>>>>

\ccsdesc{Music, Typing Efficiency} % Update this
\keywords{Typing Efficiency with Music, Cognitive Function} % placeholder text for the time being
\maketitle

@@

\section{Methodology}
After going through all the consent forms, the user will take the typing test. It will pull lyrics from popular songs and display in a graphical user interface (GUI). 
The interface will calculate the speed and accuracy in the backend of the program with the user just having to take the test. They will take the test (NUMBER OF LEVELS OF MUSIC)
while they take the test with music and no music. They will then move on the the QBTest?. % This will need to be re-written.

This is a placeholder for a citation cos otherwise the compiler throws errors \cite{AudioDistractionsAshley}.
